
\documentclass[margin,line]{res}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[bookmarksnumbered, unicode, pdftex]{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\renewcommand{\namefont}{\LARGE\bf}

\begin{document}

\name{Mikhail Glushenkov \vspace*{.1in}}

\begin{resume}
      \section{\sc Contact Information}
      \vspace{.05in}
      \begin{tabular}{@{}p{3in}p{4in}}
            London, UK                                                                                          \\
            +447535520964                                                   &
            \href{mailto:mikhail.glushenkov@gmail.com}{\texttt{mikhail.glushenkov@gmail.com}}                   \\
            GitHub: \href{https://github.com/23Skidoo}{github.com/23Skidoo} &
            LinkedIn: \href{https://www.linkedin.com/in/mikhail-glushenkov}{linkedin.com/in/mikhail-glushenkov} \\
      \end{tabular}

      \section{\sc Summary}
      Backend Engineer with 5+ years building high-throughput platforms.
      Experience with functional and systems programming languages, distributed
      systems, and cloud infrastructure on AWS.

      \section{\sc Work Experience}

       {\bf \href{https://helloprima.co.uk}{Prima UK}} \hfill {\it 2020-2025, Back-end Developer}\\
      Working on data source integration and pricing for Prima's motor insurance
      products.\\
      \begin{list}{\labelitemi}{\leftmargin=1.5em}
            \item Developed the pricing engine processing 100K+ quotes/day with low latency (Elixir/Rust).
            \item Integrated third-party data sources to improve pricing accuracy, collaborating with analysts on cross-validation.
            \item Implemented observability and monitoring, establishing best practices for logging and alerting.
            \item Built automated PySpark ETL pipelines processing 1M+ records daily for
                  reporting and analytics, ensuring data quality across systems.
            \item Mentored new joiners on the codebase, team workflows, and best practices.
      \end{list}

      {\bf \href{https://scrive.com}{Scrive AB}} \hfill {\it 2016-2020, Back-end Developer}\\
      Developing and maintaining the Scrive e-signing platform, Scrive eID Hub,
      and associated projects. Technologies: Haskell (GHC), Happstack, Servant,
      Elm.

            {\bf \href{https://haskell.org}{Haskell.org}} \hfill {\it Summers 2011,2012,2013, Google Summer of Code Student}\\
      \begin{list}{\labelitemi}{\leftmargin=1.5em}
            \item Worked on adding support for module-level parallel builds to
                  \href{https://haskell.org/cabal}{Cabal}, a system for building and
                  packaging Haskell libraries and programs.

            \item Added support for sandboxed builds and isolated environments to
                  Cabal. Sandboxing partially solves the important ``Cabal hell'' problem. Code
                  ships with Cabal since version 1.18.

            \item Parallelised the standard \texttt{cabal-install} tool, making it possible to
                  build multiple Cabal packages in parallel. Code ships with Cabal since version
                  1.16.
      \end{list}

      {\bf Codedgers Inc.} \hfill {\it 2007-2011, Software Engineer}\\
      Worked on \href{https://archive.is/ZAI8z}{Morpher}, an LLVM-based code
      obfuscator. Wrote a generic compiler driver
      (\href{https://llvm.org/releases/2.9/docs/CompilerDriver.html}{\texttt{llvmc}}). Implemented
      a dynamic software watermarking tool suite.

      \section{\sc Education}
       {\bf BSc Eng in Computer Science}, Umeå University, 2016.

      \section{\sc Open Source}

      Contributed to various open source projects including
      \href{https://github.com/haskell/cabal/}{Haskell Cabal}, \href{https://www.haskell.org/platform/}{Haskell Platform},
      \href{https://hackage.haskell.org/package/ekg}{ekg}, \href{https://llvm.org/}{LLVM}, and others.

      \section{\sc Skills}

       {\bf Languages:} Proficient in Rust, Elixir and Haskell. Familiar
      with C++, Clojure, Go, Elm, Kotlin, Java, OCaml, Python, Scala, TypeScript.\\
      {\bf Backend}: gRPC, GraphQL, REST APIs, microservices, distributed systems.\\
      {\bf Data}: PostgreSQL, Redis, DynamoDB, Kafka, Spark, Databricks.\\
      {\bf Infrastructure}: AWS (ECS, Lambda, RDS), Kubernetes, Docker, Terraform, Pulumi.\\
      {\bf Observability}: Datadog, OpenTelemetry.

      \section{\sc Misc}

      Nationality: Swedish, eligible to work in UK and EU/EFTA countries. Settled status in UK.

\end{resume}
\end{document}
